Markdown to estimate the abundance of brain cell types with the reprocessed counts from ROSMAP cohort (with TMM-VOOM normalisation)

### 2017-02-03 code/Rmd/Mayo_RNASeq_Reprocessed_TMM_VOOM_CellProp.Rmd

```{r get.gene.symbols, cache=TRUE, include=FALSE}
backgroundGenes = data.frame(gene.id = rownames(VOOM.GENE_EXPRESSION$E)) %>%
  dplyr::mutate(ensembl_gene_id = gene.id) %>%
  tidyr::separate(ensembl_gene_id, c('ensembl_gene_id', 'position'), sep = '\\.')

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "dec2016.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")

@@

```{r plot.cellprop}
cellprop1 = as.data.frame(cellprop)
cellprop1$cogdx = COVARIATES[rownames(cellprop), 'cogdx']
cellprop1 = cellprop1 %>% 
  rownameToFirstColumn('SampleID') %>%
  dplyr::select(-`P-value`,-Correlation, -RMSE) %>%
  tidyr::gather(Celltype, Fraction, -SampleID, -cogdx) %>%
  dplyr::arrange(desc(cogdx))

p = ggplot(cellprop1, aes(x = SampleID, y = Fraction, fill = Celltype, color = cogdx)) + geom_bar(stat = 'identity')
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
# p = p + facet_grid(.~cogdx)
# p

p = ggplot(cellprop1, aes(x = Celltype, y = Fraction, color = cogdx)) + geom_boxplot()
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p
```
### Synapse store
```{r syn.store, cache=TRUE}
CODE = Folder(name = 'MAYO Cell Type Abundance with Reprocessed RNASeq', parentId = parentId)
CODE = synStore(CODE)

>>>>

```{r get.gene.symbols, include=FALSE}
backgroundGenes = data.frame(gene.id = rownames(VOOM.GENE_EXPRESSION$E)) %>%
  dplyr::mutate(ensembl_gene_id = gene.id) %>%
  tidyr::separate(ensembl_gene_id, c('ensembl_gene_id', 'position'), sep = '\\.')

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "mar2016.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")

@@

```{r plot.cellprop}
cellprop1 = as.data.frame(cellprop)
cellprop1$BrainRegion.Diagnosis = COVARIATES[rownames(cellprop), 'BrainRegion.Diagnosis']
cellprop1 = cellprop1 %>% 
  rownameToFirstColumn('SampleID') %>%
  dplyr::select(-`P-value`,-Correlation, -RMSE) %>%
  tidyr::gather(Celltype, Fraction, -SampleID, -BrainRegion.Diagnosis) %>%
  dplyr::arrange(desc(BrainRegion.Diagnosis))

p = ggplot(cellprop1, aes(x = SampleID, y = Fraction, fill = Celltype, color = BrainRegion.Diagnosis)) + geom_bar(stat = 'identity')
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
# p = p + facet_grid(.~BrainRegion.Diagnosis)
# p

p = ggplot(cellprop1, aes(x = Celltype, y = Fraction, color = BrainRegion.Diagnosis)) + geom_boxplot()
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
p
```
### Synapse store
```{r syn.store, cache=TRUE}
CODE = Folder(name = 'MAYO Cell Type Abundance with Reprocessed RNASeq', parentId = parentId)
CODE = synStore(CODE)

### 2017-02-03 code/Rmd/ROSMAP_RNASeq_Reprocessed_TMM_VOOM_CellProp.Rmd

p = ggplot(cellprop1, aes(x = SampleID, y = Fraction, fill = Celltype, color = cogdx)) + geom_bar(stat = 'identity')
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
# p = p + facet_grid(.~cogdx)
p

>>>>

p = ggplot(cellprop1, aes(x = SampleID, y = Fraction, fill = Celltype, color = cogdx)) + geom_bar(stat = 'identity')
p = p + theme(axis.text.x = element_text(angle = 90, hjust = 1))
# p = p + facet_grid(.~cogdx)
# p
